UKB Models

### 2023-09-25 ukb_mods.Rmd
fixed plots

```{r}
mean.tbv.sim <- function(df, s, ageRange){
  tbv_list <- list()
  for (i in ageRange){
      tbv.val <- df %>%
        dplyr::filter(sex == s) %>%
        sort(log_age) %>%
        dplyr::filter(log_age >= (i+0.01), log_age <= (i-0.01)) %>%
        mean(TBV)
      tbv_list <- append(tbv_list, tbv.val)
  }
  return(tbv_list)
}

@@

plot_singlestudy_centiles <- function(gamlssModel, phenotype, df, color_var)
{
  #use functions in GAMLSS repo plotting_functions.R to sim and predict
  sim <- sim.data(df) #simulate data
  pred <- centile_predict(gamlssModel, sim$dataToPredictM, sim$dataToPredictF, sim$ageRange, sim$desiredCentiles) #predict centiles

@@

  sampleCentileFan <- ggplot() +
    geom_point(aes(x=age_col, y=yvar, color=color_col), alpha=0.3) +
    scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) + 
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[1]]), alpha=0.1, linetype="dashed") +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[3]]), alpha=0.3, linetype="dashed") +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[5]]), linetype="dashed", color="#40004BFF") +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[7]]), alpha=0.3, linetype="dashed") +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[9]]), alpha=0.1, linetype="dashed") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[1]]), alpha=0.1, linetype="longdash") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[3]]), alpha=0.3, linetype="longdash") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[5]]), linetype="longdash", color="#00441BFF") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[7]]), alpha=0.3, linetype="longdash") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[9]]), alpha=0.1, linetype="longdash") +
    geom_point(aes(x=male_peak_age, y=pred$peak_M), color="#40004BFF", size=3) +
    geom_point(aes(x=female_peak_age, y=pred$peak_F), color="#00441BFF", size=3) +
    labs(title=deparse(substitute(gamlssModel))) +
    theme(legend.title = element_blank())+
    xlab(paste("Age at Scan", unit_text)) +
    ylab(deparse(substitute(phenotype)))

@@

```{r}
plot_singlestudy_centiles(m4, "GMV", ukb_df, sex_char)

>>>>

```{r}
mean.tbv.sim <- function(df, s, ageRange){
  tbv_list <- list()
  for (i in ageRange){
      tbv.df <- df %>%
        dplyr::filter(sex == s) %>%
        arrange(log_age) %>%
        dplyr::filter(log_age >= (i-0.005) & log_age <= (i+0.005)) %>%
        summarize(m = mean(TBV, na.rm = TRUE))
      tbv.val <-tbv.df$m
      tbv_list <- append(tbv_list, tbv.val)
  }
  return(unlist(tbv_list))
}

@@

plot_singlestudy_centiles <- function(gamlssModel, phenotype, df, color_var)
{
  #use functions in GAMLSS repo plotting_functions.R to sim and predict
  sim <- sim.data.ukb(df) #simulate data
  pred <- centile_predict(gamlssModel, sim$dataToPredictM, sim$dataToPredictF, sim$ageRange, sim$desiredCentiles) #predict centiles

@@

  sampleCentileFan <- ggplot() +
    geom_point(aes(x=age_col, y=yvar, color=color_col), alpha=0.3) +
    scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) + 
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[1]]), alpha=0.1) +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[2]]), alpha=0.3) +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[3]]), color="#40004BFF") +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[4]]), alpha=0.3) +
    geom_line(aes(x=ages, y=pred$fanCentiles_M[[5]]), alpha=0.1) +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[1]]), alpha=0.1) +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[2]]), alpha=0.3) +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[3]]), color="#00441BFF") +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[4]]), alpha=0.3) +
    geom_line(aes(x=ages, y=pred$fanCentiles_F[[5]]), alpha=0.1) +
    geom_point(aes(x=male_peak_age, y=pred$peak_M), color="#40004BFF", size=3) +
    geom_point(aes(x=female_peak_age, y=pred$peak_F), color="#00441BFF", size=3) +
    labs(title=deparse(substitute(gamlssModel))) +
    theme(legend.title = element_blank())+
    xlab(paste("Age at Scan", unit_text)) +
    ylab(deparse(substitute(phenotype)))

@@

```{r}
plot_singlestudy_centiles(m4, "GMV", ukb_df, "sex")
